<span style="font-variant: small-caps;"><b><big>Supplement B</big></b></span>

### 2025-05-14 03-post-process/output-plots-children/01-mcmc-dims-runtime.Rmd

@@

# render the table
kable(df, format.args = list(big.mark = ","), caption = "MCMC sampling dimensions and run time.", col.names = c(" ", " "), escape = FALSE) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "condensed")) |>
  group_rows("Dimensions", start_row = min(which(groups == 1)), end_row = max(which(groups == 1))) |>
  group_rows("Per Chain", start_row = 1, end_row = 3, escape = FALSE) |>
  group_rows("Overall", start_row = 4, end_row = max(which(groups == 1))) |>
  group_rows("Run Time", start_row = min(which(groups == 2)), end_row = max(which(groups == 2)))
```

>>>>

**Model Scenario Name**: ``r params$scenario``

The table below displays MCMC sampling dimensions and run time.

@@

# render the table
kable(df, format.args = list(big.mark = ","), col.names = c(" ", " "), escape = FALSE) |>
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "condensed")) |>
  group_rows("Dimensions", start_row = min(which(groups == 1)), end_row = max(which(groups == 1))) |>
  group_rows("Per Chain", start_row = 1, end_row = 3, escape = FALSE) |>
  group_rows("Overall", start_row = 4, end_row = max(which(groups == 1))) |>
  group_rows("Run Time", start_row = min(which(groups == 2)), end_row = max(which(groups == 2)))
```

### 2025-05-14 03-post-process/output-plots-children/11-residual-diags.Rmd

#### Why Does this Matter? {-}

@@

#### What was Calculated? {-}

@@

##### JAGS Code Example {-}

@@

<details>
<summary>Click to Show Example Code</summary>
<pre>
# priors
mu_phi ~ dbeta(1,1)
sigma_Lphi ~ dunif(0,2)
&nbsp;
for (y in 1:ny) {
  # random process
  Lphi[y] ~ dnorm(logit(mu_phi), 1/sigma_Lphi^2)
  phi[y] &lt;- ilogit(Lphi[y])
  &nbsp;
  # standardized process noise term
  phi_qresid[y] &lt;- pnorm(logit(phi[y]), logit(mu_phi), 1/sigma_Lphi^2)
  &nbsp;
  # likelihood statement for fitting model
  x_surv[y] ~ dbin(phi[y], n_tagged[y])
  &nbsp;
  # standardized observation noise term
  x_surv_qresid[y] <- pbin(x_surv[y], phi[y], n_tagged[y])
} </pre>
</details>

#### What is Shown? {-}

@@

These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.
`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`

@@

>>>>

<details>
  <summary>
    <p style="font-size:20px; display:inline">Why Does this Matter?</p>
  </summary>

@@

</details>

<details>
  <summary>
    <p style="font-size:20px; display:inline">What was Calculated?</p>
  </summary>

@@

</details>

<details>
  <summary>
    <p style="font-size:20px; display:inline">Example with JAGS Code</p>
  </summary>

@@

<pre>
# priors
mu_phi ~ dbeta(1,1)
sigma_Lphi ~ dunif(0,2)
&nbsp;
for (y in 1:ny) {
  # random process
  Lphi[y] ~ dnorm(logit(mu_phi), 1/sigma_Lphi^2)
  phi[y] &lt;- ilogit(Lphi[y])
  &nbsp;
  # standardized process noise term
  phi_qresid[y] &lt;- pnorm(logit(phi[y]), logit(mu_phi), 1/sigma_Lphi^2)
  &nbsp;
  # likelihood statement for fitting model
  x_surv[y] ~ dbin(phi[y], n_tagged[y])
  &nbsp;
  # standardized observation noise term
  x_surv_qresid[y] <- pbin(x_surv[y], phi[y], n_tagged[y])
} </pre>

</details>

<details>
  <summary>
    <p style="font-size:20px; display:inline">What is Shown?</p>
  </summary>

@@

These values were calculated for each posterior sample and were summarized as the posterior mean and 95% CRI.
They are shown at the top left of each time series plot and summarized across processes in the "Summary Tables" sections.

</details>

@@

`r if (params$include_sim_years) "**Although the time series plots show simulated years beyond the observed period, the across-year summary statistics were calculated only using years that have been monitored for at least one population.**"`

### 2025-05-14 03-post-process/output-plots-children/13-param-summaries.Rmd
Rename param summaries Rmd section
& Improve it some

@@

  axis_labels(ylab = ylab, outer = FALSE, yline = 1)
  panel_label(label_text, "topleft")
}

@@

### Year 1 {.tabset .tabset-pills}

@@

### Year 2 {.tabset .tabset-pills}

@@

### Year 3 {.tabset .tabset-pills}

>>>>

Boxplots display the posterior median as the heavy line, central 50% CRL as the box boundaries, and central 95% CRL as the whisker boundaries.

@@

  axis_labels(ylab = ylab, outer = FALSE, yline = 1)
  panel_label(label_text, "topleft")
  box(col = par("col.axis"))
}

@@

### Year-1 {.tabset .tabset-pills}

@@

### Year-2 {.tabset .tabset-pills}

@@

### Year-3 {.tabset .tabset-pills}

### 2025-05-14 03-post-process/output-plots.Rmd

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
params:
  scenario:
    label: "Scenario"
    value: "new-wul_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: TRUE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_waic:
    labels: "Include WAIC Output"
    value: FALSE
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: '<span style="font-variant: small-caps;"><b><big>Supplement B</big></b></span>'
subtitle: "<small>_A state-space model to quantify density dependence, demographic heterogeneity, and spatial synchrony in Grande Ronde Basin Chinook salmon populations_</small>"
author: |
  | <small>**Authors**: B.A. Staton <a href="https://orcid.org/0000-0002-2342-3482"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, P.P. Gibson <a href="https://orcid.org/0000-0002-9751-7895"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M. Liermann <a href="https://orcid.org/0009-0004-5019-1471"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, C. Justice <a href="https://orcid.org/0000-0003-0663-5536"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, M.J. Kaylor <a href="https://orcid.org/0000-0001-5331-9830"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, R. Sharma <a href="https://orcid.org/0000-0002-3818-9393"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a>, and S.M. White <a href="https://orcid.org/0000-0003-4918-6865"><img src="https://orcid.filecamp.com/static/thumbs/03CaAkr1LaBp5PRz-small.png"/></a></small>
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
params:
  scenario:
    label: "Scenario"
    value: "final_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: TRUE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
  include_waic:
    labels: "Include WAIC Output"
    value: FALSE
editor_options: 
  chunk_output_type: console
---

```{css, echo = FALSE}
h1 {
  color: black;
  background-color: lightgrey;
  font-size: 2.75em;
  font-variant: small-caps;
  font-weight: 700;
  text-decoration: underline;
  border-radius: 5px;
  border-color: darkslategrey;
  padding-left: 10px;
  padding-right: 10px;
  padding-bottom: 5px;
  padding-top: 5px;
}
```
